Home

### 2023-06-23 Treatment_Outcomes.Rmd
IT WORKED

---
title: "Treatment Outcome Visualization"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 1
    #code_folding: hide
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE,warning = FALSE)
# Libraries 
library(tidyverse)
library(dplyr)
library(haven)
library(ggplot2)
library(tidyr)
library("lubridate")

@@

```{r, include=FALSE}
# 1. First adjust the their values for length of stay above 40 to 40, because the measures don't go above 40 days.

Mothership_post <- Mothership %>%
  mutate(Days_complete_W = ifelse(Days_complete_1 > 40, 40,Days_complete_1),

#2. Create pre_scores
      CUXOS_pre = Day1_CUXOS,
      CUDOX_pre = Day1_CUDOS
      )

@@

    CUDOS_Score <- select(Mothership,
                      Day1_CUDOS:Day40_CUDOS)
    CUDOS_Score <- data.frame(CUDOS_Score)

  # Anxiety
    CUXOS_Score <- select(Mothership,
                      Day1_CUXOS:Day40_CUXOS)
    CUXOS_Score <- data.frame(CUDOS_Score)

    view(Mothership)

@@

Mothership <- Mothership %>%
  mutate(
    CUDOS_post = CUDOS_Score[cbind(seq_along(1:8667),CUDOS_Score$Days_complete_W)],
    CUXOS_post = CUXOS_Score[cbind(seq_along(1:8667),CUDOS_Score$Days_complete_W)]
  )

#5. create new DF with Varaibles we want

AnxDep_PrePost<- data.frame(cbind(Mothership$ID1,Mothership$Disorder_Type,CUDOS_pre,CUDOS_post,CUXOS_pre,CUXOS_post)) %>%
  filter(!is.na(Mothership$Disorder_Type))
colnames(AnxDep_PrePost)[1:2] = c("ID1","Disorder_Type")

@@

#8. Pre Post CUDOS/CUXOS Plot
ggplot(data=AnxDep_PrePost_mean,
       aes(x=factor(PrePost,level=c("Pre","Post")),y=Score,
           group=Test,color=Test))+
  geom_point(size=2.5)+
  geom_line(group=AnxDep_PrePost_mean$PrePost,size=1.5)+
  scale_x_discrete(name="Time Point")+
  scale_y_continuous(name="CUDOS/CUXOS Score")+
  ggtitle("Mean Pre and Post Scores of the Anxiety and Depression")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title = element_blank())
 # scale_color_manual(values=c("1"="#8956BB","2"="#4C4452","3"="#B1A8B9",
                             # "4"="#00BCA3","5"="#008570"),
                     #labels=c("Coping Skills","Positive Mental Health",
                             # "Functioning","Well-Being","Symptoms"))

```
Anxiety / Depression Pre_Post by disorder - line plot
```{r}
#1. Creaate new datasets with only anxiety / depresssion

@@

Depression/ Anxiety pre/ post Dumbell plots
```{r}
Pre_ANX<-ANX_PrePost_mean %>%
  filter(PrePost == "Pre")

@@

sum(as.factor(ANX_PrePost$Disorder_Type))

@@

ggplot(data=Pre_DEP,
       aes(x=Disorder_Type,y=Score,
           group=Disorder_Type,color=Disorder_Type))+
  geom_segment(aes(x=Disorder_Type, xend=Post_DEP$Disorder_Type, y=Score, yend=Post_DEP$Score),color = "#aeb6bf",
              size = 4, #Note that I sized the segment to fit the points
              alpha = .5) +
  geom_point( aes(x=Disorder_Type, y=Score), color= "#F90000", size=3.5) +
  geom_point( aes(x=Post_DEP$Disorder_Type, y=Post_DEP$Score), color= "#0CC541", size=3.5) +
  labs(title = "Mean Pre and Post Depression Scores By Disorder Type",
       subtitle = "Self Report anxiety was assessed using the CUDOS",
       caption = "Symptom severity: 0-10 (remission), 11-20 (minimal), 21-30 (mild), 31-45 (moderate), 46+ (severe)")+
  scale_y_reverse()+
  # limits = c(10, 50))+
  coord_flip() +
  theme_classic()+
  theme(#legend.position = "none",
         plot.background = element_rect(
      fill = "white",
      colour = "white"))
```

>>>>

---
title: "Treatment Outcome Visualization"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 1
    #code_folding: hide
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE,warning = FALSE)
getOption("max.print")
# Libraries 
library(tidyverse)
library(dplyr)
library(haven)
library(ggplot2)
library(tidyr)
library("lubridate")

@@

# Pre and Post Scores

## {.tabset}

### Extract pre/post scores
```{r}
# 1. First adjust the their values for length of stay above 40 to 40, because the measures don't go above 40 days.

Mothership_post <- Mothership %>%
  mutate(Days_complete_W = ifelse(Days_complete_1 > 40, 40, Days_complete_1),

#2. Create pre_scores
      CUXOS_pre = Day1_CUXOS,
      CUDOS_pre = Day1_CUDOS
      ) %>%
  filter(!is.na(Days_complete_W)) %>%
  filter(!Days_complete_W == 0)

sum(is.na(Mothership_post$Days_complete_W))

@@

    CUDOS_Score <- select(Mothership_post,
                      Day1_CUDOS:Day40_CUDOS)
    CUDOS_Score <- data.frame(CUDOS_Score)

  # Anxiety
    CUXOS_Score <- select(Mothership_post, Day1_CUXOS:Day40_CUXOS)
    CUXOS_Score <- data.frame(CUXOS_Score)

length(Mothership_post$Days_complete_W)

@@

# Mothership_post2 <- Mothership_post %>%
#   mutate(
#     CUDOS_post = CUDOS_Score[cbind(seq_along(1:8610),CUDOS_Score$Days_complete_W)],
#     CUXOS_post = CUXOS_Score[cbind(seq_along(1:8610),CUXOS_Score$Days_complete_W)]
#   )

# CUDOS_Score2=CUDOS_Score[,2:41]
# CUXOS_Score2=CUXOS_Score[,2:41]

Mothership_post <- Mothership_post %>%
  mutate(
    CUDOS_post = CUDOS_Score[cbind(c(1:8367),Mothership_post$Days_complete_W)],
    CUXOS_post = CUXOS_Score[cbind(c(1:8367),Mothership_post$Days_complete_W)]
  )

####WTF
```

```{r}
#5. create new DF with Varaibles we want

AnxDep_PrePost <- data.frame(cbind(Mothership_post$ID1,
                                  Mothership_post$Disorder_Type,
                                  Mothership_post$CUDOS_pre,
                                  Mothership_post$CUDOS_post,
                                  Mothership_post$CUXOS_pre,
                                  Mothership_post$CUXOS_post)) %>%
  filter(!is.na(Mothership_post$Disorder_Type))

colnames(AnxDep_PrePost) = c("ID1","Disorder_Type", "CUDOS_pre","CUDOS_post","CUXOS_pre","CUXOS_post")

@@

### Overall Plot
```{r}
# Pre Post CUDOS/CUXOS Plot
ggplot(data=AnxDep_PrePost_mean,
       aes(x=factor(PrePost,level=c("Pre","Post")),y=Score,
           group=Test,color=Test))+
  geom_point(size=2.5)+
  geom_line(group=AnxDep_PrePost_mean$PrePost,size=1.5)+
  scale_x_discrete(name="Time Point")+
  scale_y_continuous(name="CUDOS/CUXOS Score")+
  ggtitle("Mean Pre and Post Scores of the Anxiety and Depression")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title = element_blank())

### Line Plot By Disorder
```{r}
#1. Creaate new datasets with only anxiety / depresssion

@@

### Dumbell Plot by Disorder
```{r}
Pre_ANX<-ANX_PrePost_mean %>%
  filter(PrePost == "Pre")

@@

#sum(as.factor(ANX_PrePost$Disorder_Type))

@@

ggplot(data=Pre_DEP,
       aes(x=Disorder_Type,y=Score,
           group=Disorder_Type,color=Disorder_Type))+
  geom_segment(aes(x=Disorder_Type, xend=Post_DEP$Disorder_Type, y=Score, yend=Post_DEP$Score),color = "#aeb6bf",
              size = 4, #Note that I sized the segment to fit the points
              alpha = .5) +
  geom_point( aes(x=Disorder_Type, y=Score), color= "#F90000", size=3.5) +
  geom_point( aes(x=Post_DEP$Disorder_Type, y=Post_DEP$Score), color= "#0CC541", size=3.5) +
  labs(title = "Mean Pre and Post Depression Scores By Disorder Type",
       subtitle = "Self Report anxiety was assessed using the CUDOS",
       caption = "Symptom severity: 0-10 (remission), 11-20 (minimal), 21-30 (mild), 31-45 (moderate), 46+ (severe)",
       ylab = "Disorder Type")+
  scale_y_reverse()+
  # limits = c(10, 50))+
  coord_flip() +
  theme_classic()+
  theme(#legend.position = "none",
         plot.background = element_rect(
      fill = "white",
      colour = "white"))
```

### 2023-06-23 index.Rmd
IT WORKED

>>>>

#### Enjoy my favorite visualizations from the project!

![](images/Treatment_duration.png)

![Note. Other = OCD, Eating Disorders, Somatic Disorders, and Psychotic Disorders; None = No other co-occuring disorder.](images/Co_occuring.png)

![Pre (red) and Post (green) scores of depression via self report for different DSM diagnoses.](images/Pre_post.png)
